### 2020-02-06 thesis/paper.tex
meta-vie intro

\section{Meta-View and Consensus Clustering}
bla

>>>>

\section{Meta-View and Consensus Clustering}
With either a clustering result loaded in or clustering algorithms run and the meta-clustering performed the meta-view is shown. This view allows the user to comparatively explore the clustering results, here interchangeably the term base clusterings is used, and thereby analyze their robustness. This should empower the used to make educated choices on which clustering to pick as result or to decide on which ones should be combined into a consensus result.
